\begin{thebibliography}{99}

\bibitem{andrews2015}
D.~Andrews, K.~Bonner, A.~Butterworth, H.~Calber, B.~Craddock, S.~Diber, et~al.,
\newblock Defining a successful commercial asteroid mining program,
\newblock Acta Astronautica 108 (2015) 106--118.

\bibitem{argote1990}
L.~Argote, D.~Epple,
\newblock Learning curves in manufacturing,
\newblock Science 247~(4945) (1990) 920--924.

\bibitem{arrow2014}
K.~J.~Arrow, M.~L.~Cropper, C.~Gollier, B.~Groom, G.~M.~Heal, R.~G.~Newell, et~al.,
\newblock Should governments use a declining discount rate in project analysis?,
\newblock Review of Environmental Economics and Policy 8~(2) (2014) 145--163.

\bibitem{baumers2016}
M.~Baumers, P.~Dickens, C.~Tuck, R.~Hague,
\newblock The cost of additive manufacturing: Machine productivity, economies of scale and technology-push,
\newblock Technological Forecasting and Social Change 102 (2016) 193--201.

\bibitem{benkard2000}
C.~L.~Benkard,
\newblock Learning and forgetting: The dynamics of aircraft production,
\newblock American Economic Review 90~(4) (2000) 1034--1054.

\bibitem{cesaretti2014}
G.~Cesaretti, E.~Dini, X.~De~Kestelier, V.~Colla, L.~Pambaguian,
\newblock Building components for an outpost on the lunar soil by means of a novel 3D printing technology,
\newblock Acta Astronautica 93 (2014) 430--450.

\bibitem{cilliers2023}
J.~Cilliers, A.~Rasera, S.~Hadler,
\newblock Mineralogical and chemical processing of lunar regolith for ISRU,
\newblock Minerals Engineering 194 (2023) 108023.

\bibitem{crawford2015}
I.~A.~Crawford,
\newblock Lunar resources: A review,
\newblock Progress in Physical Geography 39~(2) (2015) 137--167.

\bibitem{deweck2004}
O.~L.~de~Weck, R.~de~Neufville, M.~Chaize,
\newblock Staged deployment of communications satellite constellations in low Earth orbit,
\newblock Journal of Aerospace Computing, Information, and Communication 1~(3) (2004) 119--136.

\bibitem{dixit1994}
A.~K.~Dixit, R.~S.~Pindyck,
\newblock Investment Under Uncertainty,
\newblock Princeton University Press, Princeton, NJ, 1994.

\bibitem{dutton1984}
J.~M.~Dutton, A.~Thomas,
\newblock Treating progress functions as a managerial opportunity,
\newblock Academy of Management Review 9~(2) (1984) 235--247.

\bibitem{flyvbjerg2014}
B.~Flyvbjerg,
\newblock What you should know about megaprojects and why: An overview,
\newblock Project Management Journal 45~(2) (2014) 6--19.

\bibitem{kavlak2018}
G.~Kavlak, J.~McNerney, J.~E.~Trancik,
\newblock Evaluating the causes of cost reduction in photovoltaic modules,
\newblock Energy Policy 123 (2018) 700--710.

\bibitem{elvis2012}
M.~Elvis,
\newblock Let's mine asteroids---for science and profit,
\newblock Nature 485 (2012) 549.

\bibitem{hecht2021}
M.~Hecht, J.~Hoffman, D.~Rapp, et~al.,
\newblock Mars Oxygen ISRU Experiment (MOXIE),
\newblock Space Science Reviews 217 (2021) 9.

\bibitem{ishimatsu2016}
T.~Ishimatsu, O.~L.~de~Weck, J.~A.~Hoffman, Y.~Ohkami, R.~Shishko,
\newblock Generalized multicommodity network flow model for the Earth--Moon--Mars logistics system,
\newblock Journal of Spacecraft and Rockets 53~(1) (2016) 25--38.

\bibitem{kaplan1958}
E.~L.~Kaplan, P.~Meier,
\newblock Nonparametric estimation from incomplete observations,
\newblock Journal of the American Statistical Association 53~(282) (1958) 457--481.

\bibitem{jones2018}
H.~W.~Jones,
\newblock The recent large reduction in space launch cost,
\newblock in: 48th International Conference on Environmental Systems, ICES-2018-81, 2018.

\bibitem{jones2020}
H.~W.~Jones,
\newblock The cost of space launch: History and outlook,
\newblock in: 50th International Conference on Environmental Systems, ICES-2020-415, 2020.

\bibitem{jones2022}
H.~W.~Jones,
\newblock The cost and weight of space launch for space solar power,
\newblock in: 51st International Conference on Environmental Systems, ICES-2022-164, 2022.

\bibitem{kornuta2019}
D.~Kornuta, A.~Abbud-Madrid, J.~Atkinson, et~al.,
\newblock Commercial lunar propellant architecture: A collaborative study of lunar propellant production,
\newblock REACH 13 (2019) 100026.

\bibitem{lsic2021}
Lunar Surface Innovation Consortium,
\newblock Lunar ISRU Technology Roadmap,
\newblock Johns Hopkins Applied Physics Laboratory, 2021.

\bibitem{metzger2013}
P.~T.~Metzger, A.~Muscatello, R.~P.~Mueller, J.~Mantovani,
\newblock Affordable, rapid bootstrapping of the space industry and solar system civilization,
\newblock Journal of Aerospace Engineering 26~(1) (2013) 18--29.

\bibitem{nagy2013}
B.~Nagy, J.~D.~Farmer, Q.~M.~Bui, J.~E.~Trancik,
\newblock Statistical basis for predicting technological progress,
\newblock PLoS ONE 8~(2) (2013) e52669.

\bibitem{nasa2015handbook}
NASA,
\newblock NASA Cost Estimating Handbook, Version 4.0,
\newblock NASA Office of the Chief Financial Officer, Washington, DC, 2015.

\bibitem{oneill1974}
G.~K.~O'Neill,
\newblock The colonization of space,
\newblock Physics Today 27~(9) (1974) 32--40.

\bibitem{oneill1976}
G.~K.~O'Neill,
\newblock The High Frontier: Human Colonies in Space,
\newblock William Morrow, New York, 1976.

\bibitem{rubin2015}
E.~S.~Rubin, I.~M.~L.~Azevedo, P.~Jaramillo, S.~Yeh,
\newblock A review of learning rates for electricity supply technologies,
\newblock Energy Policy 86 (2015) 198--218.

\bibitem{saleh2003}
J.~H.~Saleh, D.~E.~Hastings, D.~J.~Newman,
\newblock Flexibility in system design and implications for aerospace systems,
\newblock Acta Astronautica 53~(12) (2003) 927--944.

\bibitem{sanders2015}
G.~B.~Sanders, W.~E.~Larson,
\newblock Progress made in lunar in situ resource utilization under NASA's Exploration Technology and Development Program,
\newblock Journal of Aerospace Engineering 28~(1) (2015) 04014075.

\bibitem{sonter1997}
M.~J.~Sonter,
\newblock The technical and economic feasibility of mining the near-Earth asteroids,
\newblock Acta Astronautica 41~(4--10) (1997) 637--647.

\bibitem{sowers2021}
G.~F.~Sowers,
\newblock The business case for lunar ice mining,
\newblock New Space 9~(2) (2021) 77--94.

\bibitem{sowers2023}
G.~F.~Sowers,
\newblock A cislunar economic framework,
\newblock New Space 11~(1) (2023) 5--18.

\bibitem{thompson2012}
P.~Thompson,
\newblock The relationship between unit cost and cumulative quantity and the evidence for organizational learning-by-doing,
\newblock Journal of Economic Perspectives 26~(3) (2012) 203--224.

\bibitem{werkheiser2015}
N.~Werkheiser, J.~Dunn, M.~Snyder, J.~Edmunson, K.~Cooper, M.~Johnston,
\newblock 3D printing in zero-G ISS technology demonstration,
\newblock in: AIAA SPACE 2015, AIAA-2015-4585, 2015.

\bibitem{wertz2011}
J.~R.~Wertz, D.~F.~Everett, J.~J.~Puschell (Eds.),
\newblock Space Mission Engineering: The New SMAD,
\newblock Microcosm Press, Hawthorne, CA, 2011.

\bibitem{wright1936}
T.~P.~Wright,
\newblock Factors affecting the cost of airplanes,
\newblock Journal of the Aeronautical Sciences 3~(4) (1936) 122--128.

\bibitem{zapata2019}
E.~Zapata,
\newblock An assessment of cost improvements in the NASA COTS/CRS program and implications for future NASA missions,
\newblock in: AIAA SPACE and Astronautics Forum, AIAA-2019-4268, 2019.

\bibitem{zubrin1996}
R.~Zubrin, R.~Wagner,
\newblock The Case for Mars: The Plan to Settle the Red Planet and Why We Must,
\newblock Free Press, New York, 1996.

\end{thebibliography}
